Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-23 paper.tex
Updated Visuals
Images and tables are now shown inside the corresponding section and subsection.

@@

        \subsubsection{How does it work?} Based on the historically best candidate
        solution and the elite set, we use the Golden Ratio (shown in
        Figure~\ref{fig.golden_ratio}) to compute the distance between new individuals
        in the population, making an improved distribution. It randomly selects a
        solution from the elite set and uses the Golden Ratio to compute multiple
        solutions against the best-found candidate.

@@

>>>>

\usepackage[section]{placeins} % Forces an image to be displayed in it's section

@@

        \subsubsection{How does it work?}

            Based on the historically best candidate
            solution and the elite set, we use the Golden Ratio (shown in
            Figure~\ref{fig.golden_ratio}) to compute the distance between new individuals
            in the population, making an improved distribution. It randomly selects a
            solution from the elite set and uses the Golden Ratio to compute multiple
            solutions against the best-found candidate.

@@

            \FloatBarrier
